\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                          % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Ekaterina}{Ovcharenko}
% \title{Developer}
\address{22, Zeleny pr., apt. 207}{Moscow}{Russia}
\phone[mobile]{+7915-257-6927}
\email{katerina.ovcharenko@gmail.com}


\newcommand{\kaspersky}{\href{kaspersky.com}{Kaspersky Lab (kaspersky.com)}}
% \newcommand{\responsibilities}{\emph{Key responsibilities}:}
% \newcommand{\achievements}{\hfill\emph{Achievements}:}

\newcommand{\responsibilities}[1]{ \emph{Responsibilities}:\begin{itemize} #1\end{itemize}}
\newcommand{\achievements}[1]{ \emph{Achievements}:\begin{itemize} #1\end{itemize}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------


\begin{document}

\makecvtitle

% \section{Work Permit}
%     \hintstyle{Student Visa:} allowed to work for up to 20 hours each week\hfill 

\section{Skills}
    \cvitem{Computer languages}{Lua, Bash, Python, R, SQL, regular expressions, XML, HTML}
    \cvitem{Tools}{Flyspray, Chili Project, CVS, Git, SSH}
    \cvitem{Systems}{Linux, Windows, MacOS}
    \cvitem{Soft skills}{managing group of 15 people, customer support, teaching}
    \cvitem{Video editing}{Final Cut Pro 2, X}
    


\section{Languages}
    \hintstyle{English:} Upper Intermediate\hfill 
    \hintstyle{Russian:} Native \hfill 


\section{Experience}

\cventry{May~2012 -- present}{Head of heuristic analysis group}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Leading a group of senior spam analysts.
        \item Providing antispam heuristics for Kaspersky line of products (Kaspersky Internet Security, Kaspersky Linux Mail Securilty, Kaspersky Security for Exchange, Kaspersky SDK).
        \item Ensuring good results in products' public tests.
        \item Antispam engine development in Lua.
        \item Improving customer retention by adding a requested functionality and fine tuning the products.
        \item Supporting and developing a spam analysis toolkit, written in Perl, Lua and Bash.
        \item Blacklisting IPs by using statistics and SQL.
        \item Training senior analysts.
        \item Keeping documentation up-to-date.
    }
    \achievements {
        \item Increased the effective share of heuristics in the overall Spam detection statistics from 45\% to 70\% with:
        \begin{itemize}
            \item focusing and controlling efforts using a task management systems, namely FlySpray and Chilli Project;
            \item applying the latest approaches from IT conferences and academic papers;
            \item initializing and supervision of new spam detection approaches;
            \item collaborating with a virus analysis group.
        \end{itemize}
        \item Trained a team of senior analysts the fundamentals of Unix shell, ssh, CVS, GIT, regular expressions.
    }
}

\cventry{February~2010 -- April~2012}{Senior Spam Analyst}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Programming complex heuristics with heavy use of regular expressions.
        \item Debugging product's control logic.
        \item Automating routine tasks by writing scripts and utilities.
        \item Monitoring data from spam traps.
        \item Spam-analysts support and teaching.
        \item Second level client support.
    }
}

\cventry{January~2008 -- January~2010}{Spam Analyst}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Creating basic antispam heuristics using proprietary text patterns.
    }
}

\cventry{June~2007 -- February~2008}{Support engineer}{Countrycom (telecommunication provider)}{Moscow}{} {
    \responsibilities {
        \item Resolving network connectivity issues.
        \item Basic wiring tasks.
    }
}

\cventry{September~2001 -- April~2003}{Teacher of physics and mathematics}{Secondary school \#4}{Dolgoprudny}{} {
    \responsibilities {
        \item Running regular physics classes.
        \item Preparing students for tertiary entrance exams.
        \item Providing advanced lectures on physics and mathematics.
    }
}


\section{Education}

\cventry{2002 -- 2005}{Mathematics Teacher}{Moscow State Pedagogical University}{}{}{
    Notable attended courses:
    \begin{itemize}
        \item  Mathematical Analysis
        \item  Abstract Algebra
        \item  Analytic Geometry
        \item  Differential Geometry and Topology
        \item  Differential Calculus
        \item  Fundamentals of Probability Theory and Stochastic Processes
        \item  Mathematical Statistics
        \item  Discrete Mathematics
        \item  Mathematical Logic
        \item  Elementary Mathematics
    \end{itemize}
}  
\cventry{1997 -- 1999}{Applied Mathematics an Physics}{Moscow Institute of Physics and Technology}{}{}{
        Notable attended courses:
    \begin{itemize}
        \item Linear Algebra and Analytical Geometry
        \item Mathematical Analysis
        \item General Physics
        \item Theoretical Mechanics
        \item Complex Analysis
        \item General and Applied Economics
        \item Informatics and Application of Computers in Academic Researches
    \end{itemize}
}

\section{Interests}
Online learning, video editing, kayaking, rafting, boardgames


% 
% \section{References}
% \begin{cvcolumns}
%   \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%   \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%   \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
% \end{cvcolumns}
% 


\end{document}

