\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                          % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% cvreferences
\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}

% personal data
\name{Ekaterina}{Ovcharenko}
% \title{Developer}
\address{104 Parkvale road}{Karori}{Wellington}
\phone[mobile]{022 1227141}
\email{katerina.ovcharenko@gmail.com}


\newcommand{\kaspersky}{\href{kaspersky.com}{Kaspersky Lab (kaspersky.com)}}
% \newcommand{\responsibilities}{\emph{Key responsibilities}:}
% \newcommand{\achievements}{\hfill\emph{Achievements}:}

\newcommand{\responsibilities}[1]{ \emph{Responsibilities}:\begin{itemize} #1\end{itemize}}
\newcommand{\achievements}[1]{ \emph{Achievements}:\begin{itemize} #1\end{itemize}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------


\begin{document}

\makecvtitle

\section{Short resume}

For the last 11 years I have been working for Kaspersky, an anti-virus giant in the area of Spam detection.

My areas of expertise were processing raw text data with regular expressions, Linux command line tools and R scripts.

My responsibilities included writing and supporting Lua, Bash, Python and SQL code, creating test scripts, associated documentation and working with a number of issue tracking systems.

Before moving to New Zealand I led the Senior Spam Analysts team for three years which was responsible for meeting the needs of the business with limited resources.


%\section{Work Permit}
%    \hintstyle{Student Visa:} allowed to work for up to 20 hours each week\hfill 

\section{Skills}
    \cvitem{Computer languages}{Lua, Bash, R, Python, SQL, regular expressions, XML, HTML}
%    \cvitem{Tools}{Flyspray, Chili Project, CVS, Git, SSH}
%    \cvitem{Systems}{Linux, Windows, MacOS}
    \cvitem{Soft skills}{managing group of 15 people, customer support, teaching, video editing}
%    \cvitem{Video editing}{Final Cut Pro 2, X}


\section{Experience}

\cventry{October~2015 -- present}{Senior Spam Analyst}{Kaspersky Lab}{part-time}{} {
    \responsibilities {
        \item Programming complex heuristics with heavy use of regular expressions.
        \item Automating routine tasks by writing scripts and utilities.
        \item Solving uncommon problems with utils and decreasing of spam detection.
        \item Second level client support.
	\item Supporting and developing a spam analysis toolkit, written in Python, Lua and Bash.
    }
}

\cventry{May~2012 -- September~2015}{Lead of heuristic analysis group}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Leading a group of senior spam analysts.
        \item Providing antispam heuristics for Kaspersky line of product.
        \item Antispam engine development in Lua.
        \item Supporting and developing a spam analysis toolkit, written in Python, Lua, R and Bash.
	\item Leading and training senior analysts.
    }
    \achievements {
        \item Increased the effective share of heuristics in the overall Spam detection statistics from 45\% to 70\% with:
        \begin{itemize}
            \item focusing and controlling efforts using a task management systems, namely FlySpray and Chilli Project;
            \item applying the latest approaches from IT conferences and academic papers;
            \item initializing and supervision of new spam detection approaches;
        \end{itemize}
	\item Received the company award for helping the product to achieve 1st place in public test.
        \item Trained a team of senior analysts the fundamentals of Unix shell, ssh, CVS, GIT, regular expressions.
    }
}
\pagebreak
\cventry{February~2010 -- April~2012}{Senior Spam Analyst}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Programming complex heuristics with heavy use of regular expressions.
        \item Debugging product's control logic.
        \item Automating routine tasks by writing scripts and utilities.
        \item Monitoring data from spam traps.
        \item Spam-analysts support and teaching.
        \item Second level client support.
    }
}

\cventry{January~2006 -- January~2010}{Spam Analyst}{Kaspersky Lab}{Moscow}{} {
    \responsibilities {
        \item Creating basic antispam heuristics using proprietary text patterns.
    }
}

%\cventry{June~2007 -- February~2008}{Support engineer}{Countrycom (telecommunication provider)}{Moscow}{} {
%    \responsibilities {
%        \item Resolving network connectivity issues.
%        \item Basic wiring tasks.
%    }
%}

\cventry{September~2001 -- April~2003}{Teacher of physics and mathematics}{Secondary school \#4}{Dolgoprudny}{} {
    \responsibilities {
        \item Running regular physics classes.
        \item Preparing students for tertiary entrance exams.
        \item Providing advanced lectures on physics and mathematics.
    }
}


\section{Education}

% \cventry{2012 -- 2013}{Cinema director}{National Research University Higher School of Media}{}{}{}

\cventry{2002 -- 2005}{Mathematics Teacher}{Moscow State Pedagogical University}{}{}{
%     Notable attended courses:
%     \begin{itemize}
%         \item  Mathematical Analysis
%         \item  Abstract Algebra
%         \item  Analytic Geometry
%         \item  Differential Geometry and Topology
%         \item  Differential Calculus
%         \item  Fundamentals of Probability Theory and Stochastic Processes
%         \item  Mathematical Statistics
%         \item  Discrete Mathematics
%         \item  Mathematical Logic
%         \item  Elementary Mathematics
%     \end{itemize}
}  
\cventry{1997 -- 1999}{Applied Mathematics an Physics}{Moscow Institute of Physics and Technology}{}{}{
%         Notable attended courses:
%     \begin{itemize}
%         \item Linear Algebra and Analytical Geometry
%         \item Mathematical Analysis
%         \item General Physics
%         \item Theoretical Mechanics
%         \item Complex Analysis
%         \item General and Applied Economics
%         \item Informatics and Application of Computers in Academic Researches
%     \end{itemize}
}

\section{Interests}
Online learning, video editing, kayaking, rafting, boardgames, LARP, guitar



\section{References}
 \begin{cvcolumns}
   \cvcolumn{\\Kaspersky Lab \\}{\begin{itemize}
		\item Dmitry Shiltsov \\Senior Developer \\d.shiltsov@gmail.com \\021 1749483 \\
		\item Evgeny Smirnov \\Head of Content Filtering Research \\Evgeny.Smirnov@kaspersky.com \\
		\item Ekaterina Willamow \\Spam Analist \\ekaterina.vylomova@fulbrightmail.org \\+61 47 8776075
			\end{itemize}}
%   \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%   \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
 \end{cvcolumns}
% 



\end{document}

